784 Lab 2: Review of Tidyverse and ggplot

### 2023-01-21 Lab 2  Tidyverse Review/Lab2_Tidyverse_Review_Answers.Rmd

+ Simple barplot example
```{r, message=FALSE, warning=FALSE}

ggplot(mtcars, aes(x=as.factor(cyl) )) + 
     geom_bar() + 
    labs(title = "Count of Cars By Cylinders", x = "Number of Cylinders", y = "Count")

ggplot(mtcars, aes(x=as.factor(cyl) )) + 
    geom_bar() + 
    labs(title = "Count of Cars By Cylinders (Horizontal)", x = "Number of Cylinders", y = "Count")+
     coord_flip()

#Grouped barplot
#Calculate percentage (and counts) of cyl by gear type
  d1<-pctgroup(mtcars,cyl,gear)
#Graph
ggplot(d1, aes(x=cyl,y=Percentage, fill=factor(gear),label=round(Percentage,digits=2))) + 
      geom_bar(position="dodge", stat="identity")+
      geom_text(size=4,vjust=-0.5,hjust=0.75,position = position_dodge(width = 1))+
      labs(title = "Percentage of Cars By Cylinders and Gear Type", x = "Number of Cylinders", y = "Percentage",fill="Gear")

@@

#calling to view top 10 
d1<-head(destinations,10)

```

```{r}
#Barplot
flight_delays<-flights %>% 
  mutate(dep_type = ifelse(dep_delay < 5, "on time", "delayed")) %>% 
   dplyr::group_by(dep_type,month) %>%
    dplyr::summarise(n = n()) %>% 
    filter(dep_type!="")

plot1<-ggplot(data=flight_delays, aes(x = factor(month),y=n, fill = dep_type)) +
  geom_bar(stat="identity")+
  labs(title="Frequency of On Time or Delayed Arrivals by Month", y="Count", fill="Type", x="Month")

### 2023-01-21 Lab 2  Tidyverse Review/Lab2_Tidyverse_Review.Rmd
Add files via upload

#Grouped barplot
#Calculate percentage (and counts) of cyl by gear type
  d1<-pctgroup(mtcars,cyl,gear)
#Graph
ggplot(d1, aes(x=cyl,y=Percentage, fill=factor(gear),label=round(Percentage,digits=2))) + 
      geom_bar(position="dodge", stat="identity")+
      labs(title = "Percentage of Cars By Cylinders and Gear Type", x = "Number of Cylinders", y = "Percentage",fill="Gear")

>>>>

#Grouped barplot
#Calculate percentage (and counts) of cyl by gear type
  d1<-pctgroup(mtcars,cyl,gear)
#Graph
ggplot(d1, aes(x=cyl,y=Percentage, fill=factor(gear),label=round(Percentage,digits=2))) + 
      geom_bar(position="dodge", stat="identity")+
      geom_text(size=4,vjust=-0.5,hjust=0.75,position = position_dodge(width = 1))+
      labs(title = "Percentage of Cars By Cylinders and Gear Type", x = "Number of Cylinders", y = "Percentage",fill="Gear")
